A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-13 article/02_Materials_and_Methods.Rmd
better figure captions

These time series also allow to derive another set of time series with a measure of cultural distance for each region-region relationship (Figure \ref{sed_region_matrix}). Cultural distance is defined here as the Squared Euclidian Distance (SED) between the trait proportions of two different regions at a certain point in time [@neimanStylisticVariationEvolutionary1995]. SED seems to be a sensible statistic here, because it is relatively simple, works with only a few assumptions and emphasises differences through squaring.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/sed_region_matrix.jpeg}
\caption{\label{sed_region_matrix}Plot matrix of the region-region squared euclidian distance time series. In the top right half for the variable \textit{burial type} and in the bottom left for the variable \textit{burial construction}.}
\end{figure*}

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean distance, correlation and mantel test results for cultural and spatial distance. Listed are the the overall mean Squared Euclidian Distances for each 200 years time slot of all region-region relations and the result statistics of the Mantel test for the variables \\textit{burial type (bt)} (\\textbf{A}) and \\textit{burial construction (bt)} (\\textbf{B}) with the spatial (sp) distance matrix (Figure \\ref{map_regions} B). (\\textbf{C}) shows the Mantel test results for the two variables if compared directly with each other.", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type & spatial distance" = 3, "burial construction & spatial distance" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "A" = 3, "B" = 3, "C" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

>>>>

These time series also allow to derive another set of time series with a measure of cultural distance for each region-region relationship (Figure \ref{sed_region_matrix}). Cultural distance is defined here as the squared euclidian distance (SED) between the trait proportions of two different regions at a certain point in time [@neimanStylisticVariationEvolutionary1995]. SED seems to be a sensible statistic here, because it is relatively simple, works with only a few assumptions and emphasises differences through squaring.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/sed_region_matrix.jpeg}
\caption{\label{sed_region_matrix}Plot matrix of the region-region squared euclidian distance time series. In the top right half for the variable \textit{burial type} and in the bottom left for the variable \textit{burial construction}. On the x-axis the time is displayed, on the y-axis the squared euclidian distance between the two relevant regions. The faint, grey line shows the actual data, the stronger, coloured line an approximation (LOESS with $span = 0.3$).}
\end{figure*}

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean distance, correlation and mantel test results for cultural and spatial distance. Listed are the the overall mean squared euclidian distances for each 200 years time slot of all region-region relations and the result statistics of the Mantel test for the variables \\textit{burial type (bt)} (\\textbf{A}) and \\textit{burial construction (bt)} (\\textbf{B}) with the spatial (sp) distance matrix (Figure \\ref{map_regions} B). (\\textbf{C}) shows the Mantel test results for the two variables if compared directly with each other.", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type & spatial distance" = 3, "burial construction & spatial distance" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "A" = 3, "B" = 3, "C" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```
